Wired for Success: Sweden's Electrical Innovators in the Age of Industrial Transformation

### 2023-10-30 index.qmd
adding new affiliation

---
title: "Wired for Success: Sweden's Electrical Innovators in the Age of Industrial Transformation"
subtitle: "Presentation at SDU for the group working on Human Capital in the Nordic Countries"
author: "Jonathan Jayes  - Lund University"
title-slide-attributes:
  data-background-image: "assets/preview.png"
  data-background-size: "30%"
  data-background-opacity: "0.6"
format: 
  revealjs:
    code-overflow: wrap
    width: 1600
    height: 900
    fig-align: center
    default-image-extension: svg
    footer: "[{{< fa house >}}](https://interludeone.com)"
    slide-number: c
    code-block-bg: true
    code-block-border-left: "#31BAE9"
image: "preview_img/03-coordinate-systems-and-axes.jfif"
favicon: html/favicon.ico
---

@@

>>>>

---
title: "Wired for Success: Sweden's Electrical Innovators in the Age of Industrial Transformation"
subtitle: "Presentation on Social Mobility - Wicksell 30/10/2023"
author: "Jonathan Jayes  - Lund University"
title-slide-attributes:
  data-background-image: "assets/preview.png"
  data-background-size: "30%"
  data-background-opacity: "0.6"
format: 
  revealjs:
    code-overflow: wrap
    width: 1600
    height: 900
    fig-align: center
    default-image-extension: svg
    footer: "[{{< fa house >}}](https://interludeone.com)"
    slide-number: c
    code-block-bg: true
    code-block-border-left: "#31BAE9"
image: "preview_img/03-coordinate-systems-and-axes.jfif"
favicon: html/favicon.ico
---

@@

## Matricies of HISCO codes

```{python}
import plotly.express as px
import numpy as np

# Generate random transition matrix
np.random.seed(42)
num_classes = 7
transition_matrix = np.random.randint(0, 100, (num_classes, num_classes))

# Define class labels
class_labels = [f"HISCLASS {i+1}" for i in range(num_classes)]

# Create heatmap
fig = px.imshow(
    transition_matrix,
    labels=dict(x="From", y="To", color="Count"),
    x=class_labels,
    y=class_labels,
    color_continuous_scale='Viridis',
    title="Transition Counts between HISCLASS"
)

# Show heatmap
fig.show()
